---
title: "Analysis on non-smoothed images"
author: "Marco Palma"
date: "`r format(Sys.Date(),'%d')` March 2020"
output: 
  editor_options: 
    chunk_output_type: console
  html_notebook:
    code_folding: hide
    highlight: tango
    theme: readable
  html_document:
    keep_md: true
    theme: readable
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
    number_sections: true
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    fig_crop: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, tidy = TRUE
                      #, dev = "pdf", fig.path = "figures_TBM/"
                      )

options(digits = 3)
```

## Packages

```{r packages}
start_time <- Sys.time()

library(bigmemory)
library(bigstatsr)
library(ggplot2)
library(MASS)
library(dplyr)
library(e1071)
library(oro.nifti)
library(neurobase)

```

The following chunk is needed only the first time that you try to use your big file. It will create the .bin and the .desc file that you can use next time for fast loading.

```{r, echo = TRUE, eval = FALSE}
x <- read.big.matrix("data_masked.dat",
                     sep = " ", header = FALSE,
                     type = "integer",
                     has.row.names = TRUE,
                     backingfile = "tbm_data.bin", 
                     descriptorfile = "tbm_data.desc")
```


## Plots

```{r import_data}
xdesc <- dget("tbm_data.desc")

tbm_data <- attach.big.matrix(xdesc)

data_PTID <- read.table("data_PTID.txt", quote="\"", comment.char="")$V1 %>%
  as.character()

#dim(tbm_data[])
#tbm_data[1:3,1:5]
```

```{r summary_stats, cache=TRUE}
tbm_data_FBM <- big_copy(tbm_data)
#tbm_data_FBM <- big_copy(tbm_data, type = "unsigned short")
#system.time(summary_tbm <- big_colstats(tbm_data_FBM))
#summary_tbm$mean <- summary_tbm$sum/817

stats_scale <- big_scale(center = TRUE, scale = TRUE)(tbm_data_FBM)


#colskew <- function(X, ind) Rfast::colskewness(X[, ind])
colskew <- function(X, ind) timeSeries::colSkewness(X[, ind])
#colskew <- function(X, ind) e1071::skewness(X[, ind], type = 3)
skewness <- big_apply(tbm_data_FBM, a.FUN = colskew, a.combine = 'c')


stats_scale <- cbind(stats_scale, skewness)

```

Skewness measure:

$$\dfrac{nm_3}{(n-1)(n-2)(\frac{m_2}{n-1})^{3/2}}=\dfrac{n\sqrt{n-1}}{n-2}\dfrac{m_3}{m_2^{3/2}}$$
```{r neurofundata}
devtools::install_github("marcopalma3/neurofundata") #, force = TRUE)
library(neurofundata)
```

```{r plots_summary, fig.show='hold', out.width = "33%"}
theme_set(
    theme_classic(base_size = 18)
)

ggplot(stats_scale/1000, aes(center,scale)) +
  geom_bin2d(bins = 600) +
  scale_fill_continuous(type = "viridis") +
  stat_smooth(color = 2, fill = "yellow") +
  labs(x = "Voxelwise mean", y = "Voxelwise SD", title = "Rescaled TBM images (divided by 1000)")

ggplot(stats_scale, aes(center,skewness)) +
  geom_bin2d(bins = 600) +
  scale_fill_continuous(type = "viridis") +
  stat_smooth(color = 2, fill = "yellow") +
  labs(x = "Voxelwise mean", y = "Voxelwise skewness", fill="Count"#, title = "Rescaled TBM images"
  )

ggplot(stats_scale, aes(center, scale)) +
  geom_point(aes(color = skewness), alpha = 5/10, size=1, shape=".") + 
  scale_color_continuous(type = "viridis") +
  labs(x = "Voxelwise mean", y = "Voxelwise SD", color = "Voxelwise\nskewness") + #, title = "Rescaled TBM images") +
  theme_classic(base_size = 20)

```

```{r function_pred_REV, echo=FALSE, eval = FALSE}

resize_image <- function(mask, img = mask){
  mask <- drop(mask)
  img <- drop(img)
  dims <- dim(mask)
  
  if(!all.equal(dim(img), dims)) stop("Mask and img must have the same dimensions!")
  
  nonzero_coord <- matrix(NA, nrow = length(dims), ncol = 2)
  rownames(nonzero_coord) <- paste0("Dim", 1:length(dims))
  colnames(nonzero_coord) <- c("first","last")
  
  
  for(i in 1:length(dims)) nonzero_coord[i,] <- range(which(apply(mask,i,sum) != 0))
  ###select first and last coordinate for which the sum is non zero
  
  resized_array <- (img[,,]*(mask[,,]>0))[nonzero_coord[1,"first"]:nonzero_coord[1,"last"],
                                          nonzero_coord[2,"first"]:nonzero_coord[2,"last"],
                                          nonzero_coord[3,"first"]:nonzero_coord[3,"last"]]
  
  return(list(array = resized_array, original_coord = nonzero_coord))
}

calc_projection_Bspl <- function(knot_space, mask_fname){
  
  start_time <- Sys.time()
  mask <- readNIfTI(fname = mask_fname)  %>%
    magrittr::is_greater_than(0.5)*1      ### to avoid fuzzy boundaries
  mask_subset <- resize_image(mask)
  dims_mask <- dim(mask_subset$array)
  voxel_grid_nonzero_mask<- which(as.vector(mask_subset$array) != 0)
  
  basismat_dim1 <- bsplineS(x = 1:dims_mask[1], breaks = c(seq(1,dims_mask[1], by = knot_space), dims_mask[1]), norder=3, nderiv=0, returnMatrix=TRUE)
  basismat_dim2 <- bsplineS(x = 1:dims_mask[2], breaks = c(seq(1,dims_mask[2], by = knot_space), dims_mask[2]), norder=3, nderiv=0, returnMatrix=TRUE)
  basismat_dim3 <- bsplineS(x = 1:dims_mask[3], breaks = c(seq(1,dims_mask[3], by = knot_space), dims_mask[3]), norder=3, nderiv=0, returnMatrix=TRUE)
  
  design_mat <- spam::kronecker(basismat_dim3, basismat_dim2, make.dimnames = TRUE) %>%
    spam::kronecker(., basismat_dim1, make.dimnames = TRUE) %>%
    .[voxel_grid_nonzero_mask, ]  %>%
    .[, colSums(.) != 0]
  
  #design_mat@x[design_mat@x<0.001] <- 0
  #design_mat <- design_mat[, colSums(design_mat) != 0]
  
  cat("The number of basis functions is ", ncol(design_mat),".\n", sep = "")
  
  return(list("basis_mat" = design_mat, 
              "voxel_grid_nonzero_mask" = voxel_grid_nonzero_mask, 
              "dims_mask" = dims_mask,
              "mask_subset" = mask_subset))
}

slices.plot <- function(image.vec, dims = dims_mask, 
                        voxels = results$voxel_grid_nonzero_mask, 
                        col.threshold = 0, 
                        legend.range = range(image.vec), ...){
  img <- rep(NA, prod(dims_mask))
  img[voxels] <- image.vec
  
  ybr <- seq(legend.range[1], legend.range[2], length.out = 101)

  rc1 <- colorRampPalette(colors = c("blue", "white"), space="Lab")(length(which(ybr < col.threshold)))    
  rc2 <- colorRampPalette(colors = c("white", "red"), space="Lab")(length(which(ybr > col.threshold))-1)
  rampcols <- c(rc1, rc2)
  
  if(col.threshold == 0){
    leg.text <- c(format(min(ybr), scientific = TRUE, digits = 3), 
                  col.threshold, format(max(ybr), scientific = TRUE, digits = 3))
  } else{
    leg.text <- c(floor(min(ybr)), col.threshold, ceiling(max(ybr)))
  }
  overlay(x = nifti(resize_image(mask, img_template)$array), 
          y = nifti(array(img, dim = dims_mask)), 
          plot.type="single", z = seq(16, 136, by = 5), 
          col.y = scales::alpha(rampcols, 0.45), useRaster = TRUE, oma = c(4,0,0,0))
  fields::image.plot(legend.only=TRUE, zlim= range(ybr), 
                     col = rampcols, horizontal = TRUE, 
                     legend.mar = 1.5, legend.cex=0.5, legend.width = 0.8, 
                     legend.args = list(text = leg.text,
                                        col="white", cex=0.7, side = 1, 
                                        at = c(min(ybr),col.threshold, max(ybr))))
  #par(xpd = TRUE)
  #lab_img <- 34 + seq(16, 136, by = 5)
  #annot_grid <- expand.grid(0.025 + seq(0, 0.95, by = 0.2), seq(0.97, 0.1, by = -0.175))
  #library(grid)
  #grid.text(lab_img, x=annot_grid[,1], y=annot_grid[,2],gp=gpar(fontsize=10, cex = 0.9, col = "white"))
} 


fqr_prediction <-  function(train_sub,
                            test_sub,
                            data_demo = data_ADNI_bl_817,
                            pred_table,
                            qr_pen = "LASSO",
                            qr_postLASSO = FALSE,
                            lambda = NULL,
                            tau_levels = tau_lev,
                            return_func_coef = FALSE){
  
    data_projected_train <- data_projected[train_sub,]
    data_projected_test <- data_projected[test_sub,]
    
    coef_data <- data_projected_train  %>% scale(scale = F)
    FPCA_mat <- Matrix::tcrossprod(coef_data, basis_W_half) / sqrt(nrow(coef_data) - 1)
    
    tmpSVD <- svd(FPCA_mat, nu = 0)  ###, nv = 50
    values <- tmpSVD$d ^ 2

    ncomp <- which(cumsum(values) / sum(values) >= pve_threshold)[1]
    vectors <- Matrix::solve(basis_W_half, tmpSVD$v[, 1:ncomp])
    
    scores_mat <- data_projected %>%
      data.matrix(., rownames.force = TRUE) %>%
      sweep(., 2, colMeans(data_projected_train)) %>%
      magrittr::multiply_by_matrix(., int_mat) %*% vectors %>%
      as.matrix()
    
    regr_data <- scores_mat %>%
      as.data.frame(.) %>%
      tibble::rownames_to_column(., var = "PTID") %>%
      right_join(data_demo, ., by =  "PTID") %>%
      select(PTID, AGE, starts_with('V', ignore.case = FALSE)) %>% #PTGENDER2
      tibble::column_to_rownames(., "PTID")
    
    set.seed(657)
    model_lower <- rqPen::cv.rq.pen(x = as.matrix(regr_data[train_sub, -1]),
                                    y = regr_data[train_sub, ]$AGE,
                                    tau = tau_levels[1],
                                    method = "br",
                                    penalty = qr_pen#,                                   penVars = 2:(dim(regr_data)[2]-1)
                                    )
    
    model_med <- rqPen::cv.rq.pen(x = as.matrix(regr_data[train_sub, -1]),
                                  y = regr_data[train_sub, ]$AGE,
                                  tau = tau_levels[2],
                                  method = "br",
                                  penalty = qr_pen#,penVars = 2:(dim(regr_data)[2]-1)
                                  )
    
    model_upper <- rqPen::cv.rq.pen(x = as.matrix(regr_data[train_sub, -1]),
                                    y = regr_data[train_sub,]$AGE,
                                    tau = tau_levels[3],
                                    #lambda = lambda,
                                    method = "br",
                                    penalty = qr_pen#,penVars = 2:(dim(regr_data)[2]-1)
                                    )
    
    model_lower_coef <- with(model_lower, models[[which(cv[, 1] == lambda.min)]]$coefficients[-1])
    model_med_coef <- with(model_med, models[[which(cv[, 1] == lambda.min)]]$coefficients[-1])
    model_upper_coef <- with(model_upper, models[[which(cv[, 1] == lambda.min)]]$coefficients[-1])
    
    lambda_min_med <- model_med$lambda.min
    
    if (return_func_coef == TRUE)
      print(cv_plots(model_med, logLambda = TRUE, loi = NULL))
    
    if (qr_postLASSO == TRUE) {
      model_lower <- model_lower_coef %>%
        subset(., !not(.)) %>%
        when(length(names(.)) < 1  ~ 1, ~ names(.)) %>%
        paste(., collapse = "+") %>%
        paste("AGE ~ ", .) %>%
        formula(.) %>%
        rq(., tau = tau_lev[1], data = regr_data[train_sub,])
      
      model_med <- model_med_coef %>%
        subset(., !not(.)) %>%
        when(length(names(.)) < 1  ~ 1, ~ names(.))  %>%      
        paste(., collapse = "+") %>%
        paste("AGE ~ ", .) %>%
        formula(.) %>%
        rq(., tau = tau_lev[2], data = regr_data[train_sub,])
      
      model_upper <- model_upper_coef %>%
        subset(., !not(.)) %>%
        when(length(names(.)) < 1  ~ 1, ~ names(.))  %>%
        paste(., collapse = "+") %>%
        paste("AGE ~ ", .) %>%
        formula(.) %>%
        rq(., tau = tau_lev[3], data = regr_data[train_sub,])
      
      pred_table[test_sub, 1] <- model_lower %>%
        predict(newdata = regr_data[test_sub, ])
      pred_table[test_sub, 2] <- model_med %>%
        predict(newdata = regr_data[test_sub, ])
      pred_table[test_sub, 3] <- model_upper %>%
        predict(newdata = regr_data[test_sub, ])
      
    } else {
      pred_table[test_sub, 1] <- model_lower %>%
        predict(newx = as.matrix(regr_data[test_sub,-1]))
      pred_table[test_sub, 2] <- model_med %>%
        predict(newx = as.matrix(regr_data[test_sub,-1]))
      pred_table[test_sub, 3] <- model_upper %>%
        predict(newx = as.matrix(regr_data[test_sub,-1]))
    }
    
    if (return_func_coef == FALSE)
      return(pred_table)
    else
      return(list(pred_table = pred_table,
                  no_fpc = ncomp,
                  evec = vectors,
                  model_med_coef = as(model_med_coef, "sparseMatrix"),
                  model_lower_coef = as(model_lower_coef, "sparseMatrix"),
                  model_upper_coef = as(model_upper_coef, "sparseMatrix"),
                  lambda_min = lambda_min_med,
                  no_comp = ncomp
                  )
      )
  }  
```


## Summary statistics maps - ALL SUBJECTS

```{r mask_template}
load("basis_functions_12mm.RData")

mask <- readNIfTI(fname = "smoothed_mask_125.nii.gz")
fn = "ADNI_ICBM9P_mni_4step_MDT.img"
dimscan <- c(220,220,220)
img_template <- array(readBin(fn, what = "int", n = prod(dimscan), size = 2, signed = FALSE), dim = dimscan)
```

```{r summary_maps}

slices.plot(stats_scale$center, voxels = voxel_grid_nonzero_mask, col.threshold = 1000, slice_number = FALSE)

slices.plot(stats_scale$scale/1000, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale$scale/1000, 0.75), 3))

slices.plot(stats_scale$skewness, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale$skewness, 0.75), 3))
```


## Plots by diagnosis #######################

```{r ADNI_bl}
load("ADNI_bl.RData")

#all.equal(as.factor(sort(data_ADNI_bl_817$PTID)), data_PTID$V1)
ADNI_demo <- data_ADNI_bl_817[order(data_ADNI_bl_817$PTID), c("AGE", "Dx")]
rownames(ADNI_demo) <- sort(data_ADNI_bl_817$PTID)

all.equal(sort(data_ADNI_bl_817$PTID), data_PTID)
```

```{r summary_stats_Dx, cache=TRUE}

tbm_data_FBM_CN <- big_copy(tbm_data, ind.row = which(ADNI_demo$Dx == "N"))
stats_scale_CN <- big_scale(center = TRUE, scale = TRUE)(tbm_data_FBM_CN)
#stats_scale_CN$skewness <- big_apply(tbm_data_FBM_CN, a.FUN = colskew, a.combine = 'c')

tbm_data_FBM_MCI <- big_copy(tbm_data, ind.row = which(ADNI_demo$Dx == "MCI"))
stats_scale_MCI <- big_scale(center = TRUE, scale = TRUE)(tbm_data_FBM_MCI)
#stats_scale_MCI$skewness <- big_apply(tbm_data_FBM_MCI, a.FUN = colskew, a.combine = 'c')

tbm_data_FBM_AD <- big_copy(tbm_data, ind.row = which(ADNI_demo$Dx == "AD"))
stats_scale_AD <- big_scale(center = TRUE, scale = TRUE)(tbm_data_FBM_AD)
#stats_scale_AD$skewness <- big_apply(tbm_data_FBM_AD, a.FUN = colskew, a.combine = 'c')

```

```{r summary_plots_Dx, fig.show='hold', out.width = "33%"}

theme_set(
    theme_classic(base_size = 18)
)

p1 <- ggplot(stats_scale_CN, aes(center,scale)) +
  geom_bin2d(bins = 600) +
  #theme(legend.position="bottom") +
  stat_smooth(color = 2, fill = "yellow") +
  scale_fill_continuous(type = "viridis", limits = c(0,1300)) +
  xlim(800, 1650) + 
  ylim(50, 800) +
  labs(x = "Voxelwise mean", y = "Voxelwise SD", title = "CN", fill = "Count")

p2 <- ggplot(stats_scale_MCI, aes(center,scale)) +
  geom_bin2d(bins = 600) +
  stat_smooth(color = 2, fill = "yellow") +
  scale_fill_continuous(type = "viridis", limits = c(0,1300)) +
  xlim(800, 1650) + 
  ylim(50, 800) +
  labs(x = "Voxelwise mean", y = "Voxelwise SD", title = "MCI")

p3 <- ggplot(stats_scale_AD, aes(center,scale)) +
  geom_bin2d(bins = 600) +
  stat_smooth(color = 2, fill = "yellow") +
  scale_fill_continuous(type = "viridis", limits = c(0,1300)) +
  xlim(800, 1650) + 
  ylim(50, 800) +
  labs(x = "Voxelwise mean", y = "Voxelwise SD", title = "AD")

cowplot::plot_grid(p1 + theme(legend.position="none")+ 
                     theme(plot.margin = unit(c(0, 0, 0, 0), "cm")),
                   p2 + theme(legend.position="none")+ 
                     theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))+
                     theme(axis.text.y = element_blank(),
                           axis.ticks.y = element_blank(),
                           axis.title.y = element_blank() ),
                   p3 + theme(legend.position="none")+
                     theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))+
                     theme(axis.text.y = element_blank(),
                           axis.ticks.y = element_blank(),
                           axis.title.y = element_blank() ),
                   cowplot::get_legend(p1), 
                   #labels = c("CN", "MCI", "AD", NULL),
                   nrow = 1, align = "v",axis = "l", rel_widths = c(1,1,1,0.6))
```

### CN

```{r summary_maps_CN}
slices.plot(stats_scale_CN$center, voxels = voxel_grid_nonzero_mask, col.threshold = 1000)

slices.plot(stats_scale_CN$scale/1000, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale_CN$scale/1000, 0.75), 3))

slices.plot(stats_scale_CN$skewness, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale_CN$skewness, 0.75), 3))
```

### MCI

```{r summary_maps_MCI}
slices.plot(stats_scale_MCI$center, voxels = voxel_grid_nonzero_mask, col.threshold = 1000)

slices.plot(stats_scale_MCI$scale/1000, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale_MCI$scale/1000, 0.75), 3))

slices.plot(stats_scale_MCI$skewness, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale_MCI$skewness, 0.75), 3))
```

### AD

```{r summary_maps_AD}
slices.plot(stats_scale_AD$center, voxels = voxel_grid_nonzero_mask, col.threshold = 1000)

slices.plot(stats_scale_AD$scale/1000, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale_AD$scale/1000, 0.75), 3))

slices.plot(stats_scale_AD$skewness, voxels = voxel_grid_nonzero_mask,
            col.threshold = round(quantile(stats_scale_AD$skewness, 0.75), 3))
```


## Distribution for specifically selected voxels

```{r singlevoxel, fig.show='hold', out.width = "33%" }

voxel_index <- c(which.max(stats_scale$scale), which.min(stats_scale$scale))
            #,which.max(stats_scale$scale)+56,sample(nrow(stats_scale), size = 2))
hist(tbm_data[ ,voxel_index[1]], "FD")
plot(tbm_data[ ,voxel_index[1]], tbm_data[ ,voxel_index[1]+1])
plot(tbm_data[ ,voxel_index[1]], tbm_data[ ,voxel_index[1]+10])
hist(tbm_data[ ,voxel_index[2]], "FD")
plot(tbm_data[ ,voxel_index[2]], tbm_data[ ,voxel_index[2]+1])
plot(tbm_data[ ,voxel_index[2]], tbm_data[ ,voxel_index[2]+10])

voxel_demo <- data.frame(ADNI_demo, "Voxel" = tbm_data[ ,voxel_index])


grid_all <- expand.grid(x = 1:dims_mask[1], y = 1:dims_mask[2], z = 1:dims_mask[3],                      KEEP.OUT.ATTRS = FALSE)

location <- voxel_grid_nonzero_mask[voxel_index] %>%
  grid_all[., ] 



#orthographic(oro.nifti::nifti(resize_image(mask, img_template)$array), y = NULL, xyz = as.numeric(location))
#image(nifti(img_template), z=140, plot.type = "single")

#imgMASKED <- mask_img(img_template, mask, allow.NA = TRUE)
# image(nifti(imgMASKED), z=140, plot.type = "single")
# 
# dim_list <- getEmptyImageDimensions(mask, value = 0, threshold = 0, reorient = FALSE)
# 
# grid_orig <- expand.grid("x" = dim_list[[1]], 
#                    "y" = dim_list[[2]], 
#                    "z" = dim_list[[3]],
#                    KEEP.OUT.ATTRS = FALSE)

library(neurobase)
template_resized <- mask_img(img_template, mask, allow.NA = TRUE) %>%
  dropEmptyImageDimensions(., value = 0, threshold = 0, reorient = FALSE)

```

```{r index2array, echo=FALSE}
#index2array <- function(image_vec, dims, voxels){
  #img <- rep(NA, prod(dims))
  #img[voxels] <- image_vec
  #array(img, dim = dims)
  #grid_all <- expand.grid(x = 1:dims[1], y = 1:dims[2], z = 1:dims[3])
  #grid_all$value <- NA
  #grid_all$value[voxels] <- image_vec
  #if(position <= prod(dims) && position >= 1) print(grid_all[position, ])
#}
```


## Are these summary statistics smooth?

```{r grid_stats_line, fig.show='hold', out.width = "33%"}
grid_stats <- matrix(NA, nrow=nrow(grid_all), ncol=3)

grid_stats[voxel_grid_nonzero_mask, 1] <- stats_scale$center
grid_stats[voxel_grid_nonzero_mask, 2] <- stats_scale$scale 
grid_stats[voxel_grid_nonzero_mask, 3] <- stats_scale$skewness 


as.vector(location[1,2:3])
grid_stats_line <- which(grid_all$y == location[1,2] & 
                           grid_all$z == location[1,3]) %>%
  grid_stats[., ] %>%
  as.data.frame()

dim(grid_stats_line)
names(grid_stats_line) <- c("center", "scale", "skewness")



data_grid <- data.frame(x=1:151, grid_stats_line)

data_grid <- data_grid[complete.cases(data_grid),]

with(data_grid, plot(x,center))
lines(predict(smooth.spline(data_grid$x, data_grid$center, spar=0.35)), col='red', lwd=2)

with(data_grid, plot(x,scale))
lines(predict(smooth.spline(data_grid$x, data_grid$scale, spar=0.35)), col='red', lwd=2)

with(data_grid, plot(x,skewness))
lines(predict(smooth.spline(data_grid$x, data_grid$skewness, spar=0.35)), col='red', lwd=2)


```


## Distribution for each voxel by diagnosis

```{r voxel_highSD, fig.show='hold', out.width = "33%"}
my_pal <- c("#009E73", "gold3", "#D55E00")
#my_pal <- c("darkblue", "gold3", "#D55E00")

theme_set(
    theme_classic(base_size = 20)
)


old.par <- par(no.readonly = TRUE)

for (i in 1:nrow(location)){

orthographic(template_resized, y = NULL, xyz = as.numeric(location[i,]))

# p1 <- ggplot(data = voxel_demo, aes_string(x=paste0("Voxel.",i),  color = "Dx")) +
#   geom_density(position="identity", alpha=0.25)+
#   geom_vline(xintercept=1000, lty = 2) +
#   scale_color_manual(name = "Diagnosis",
#                      values = rev(my_pal), guide = guide_legend(reverse = TRUE,
#                                           override.aes = list(alpha = 1,
#                                                               size = 0.9)))


p2 <- ggplot(data = voxel_demo,  aes_string(x=paste0("Voxel.",i),  color = "Dx")) + 
  geom_step(stat="ecdf") + 
  geom_vline(xintercept=1000, lty = 2) +
  labs(x = paste("TBM at voxel", voxel_index[i]), y = "CDF")+ #,title = "ECDF for different Dx") + 
  scale_color_manual(name = "Diagnosis",
                     labels = c("AD", "MCI", "CN"),
                     values = rev(my_pal), guide = guide_legend(reverse = TRUE,
                                          override.aes = list(alpha = 1,
                                                              size = 0.9)))

#print(p1)
print(p2)

# ggplot(data = voxel_demo, aes(x = Voxel, 
#                             #fill = fct_rev(Dx), 
#                             color = Dx #fct_rev(Dx)
#                             )) + 
#   stat_bin(geom="step", bins = nclass.FD(voxel_demo$Voxel),
#            direction="vh",
#            position = "identity", size = 1.2, alpha = 0.5, pad = TRUE
#            )+
#   labs(x = paste("TBM at voxel", voxel_index)) +
#   scale_color_manual(name = "Diagnosis",
#                      values = rev(my_pal),
#                      guide = guide_legend(reverse = TRUE,
#                                           override.aes = list(alpha = 1,
#                                                               size = 0.9))) + 
#   theme_classic() +131
#   geom_hline(yintercept = 0, colour = "white", size = 1.5) +
#   expand_limits(y = 0) +
#   scale_y_continuous(expand = c(0, 0)) +
#   geom_vline(xintercept = 1000, lty = 2)

}
```


## END

```{r end_time}
Sys.time() - start_time
```

```{r, cache = TRUE, echo = FALSE, eval = FALSE}
ADNI_demo$predicted <- NA

ADNI_demo_CN <- ADNI_demo[which(ADNI_demo$Dx == "N"), ]

set.seed(657)

nfolds <- 10
foldId <- cut(1:dim(tbm_data_FBM_CN)[1], breaks = nfolds, labels = F) %>%
      sample()
table(foldId)

system.time(
for(i in 1:nfolds){
  print(i)
  
  ADNI_demo_CN$predicted[which(foldId == i)] <- big_spLinReg(tbm_data_FBM_CN,
               y.train = ADNI_demo_CN$AGE[which(foldId != i)],
               ind.train = which(foldId != i),
               alphas = 1, K = 10) %>%
    predict(., tbm_data_FBM_CN,  ind.row = which(foldId == i))
}

#summary(model_CN, best.only = TRUE)
)

with(ADNI_demo_CN, mean(abs(predicted - AGE)))
```

```{r PCA_TBM, echo = FALSE, eval = FALSE}
prcomp_CN <- big_SVD(tbm_data_FBM_CN,
        fun.scaling = big_scale(center = TRUE, scale = FALSE), 
        k = 100)

plot(prcomp_CN$d^2)

big_center <- big_scale(scale = FALSE)
meanTBM <- as_FBM(big_center(tbm_data_FBM_CN))
system.time(covmat2 <- big_crossprodSelf(tbm_data_FBM_CN, 
                                         fun.scaling = big_scale(center = TRUE)))


### diagonal of the product matrix
cumsum(prcomp_CN$d^2)/sum(diag(covmat))
```
